---
title       : Slides for Developing Data Products Course
subtitle    : Shiny App
author      : Ashvani Kumar Dubey
job         : Master Of Scienece Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---      

## Data for Shiny App

1. Randomly generated observations from normal distribution with specified mean and variance.   
2. In R 1000 observations from normal distribution with mean *0* and standard deviation *1* can be generated by the following command (Data is stored in object *myData*).  

```{r, echo=TRUE, eval=TRUE}
myData <- rnorm(1000, mean = 0, sd = 1)
# first three observations
head(myData, n = 3)
```    

--- .class #id 

## Ploting Histogram in R   

1. A histogram in R can be plotted by running the following command.
```{r, fig.width=10, fig.height=5, fig.align='center'}
hist(myData, col = "cyan", prob = T)
# to plot empirical density
lines(density(myData), col = "red", lwd = "2")

```   

---    

## Shiny ui.R file  
1. Shiny ui.R has two numericInput method.   
   - First for input of mean where default mean is set to zero.   
   - Second for input of Variance where default variance is set to 1.  
2. Shiny ui.R has two sliderInput method.   
   - First for input of number of observations(default is 5000). Number of observations that can set are 100 to 10000 in steps of 100 .
   - Second for input of number of breaks(default is 50). Number of breaks that can set are 5 to 100 in steps of 5.  

---   

## Shiny server.R file   

1. Plot of histogram will be changing due to change of data or number of breaks. Hence two reactive functions are implented in server.R file.   
   - first reactive function checks change in observations which will change due to change in at least one of mean, variance and number of observations.
   - Second reactive function takes care of number of breaks.   
2. Returns plotoutput that plots histogram with specified number of breaks and an empirical density estimate colored with red.   
3. 